### 2021-10-25 paper/output/document/paper41.tex
a solution i guess

If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%

@@

\ universalized{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}universalized\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline

@@

\ not{\isacharunderscore}universalizable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}universalized\ M\ s\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isamarkupcmt{The maxim willed by subject $s$ is not universalizable if, for all people $p$, if $p$ wills M, then 
$M$ is no longer effective for $s$.%

@@

\ O{\isacharunderscore}diamond\ \isanewline
\ \ \isacommand{using}\isamarkupfalse%
\ prod{\isachardot}simps{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ split{\isacharunderscore}conv\ \isacommand{by}\isamarkupfalse%
\ fastforce%

@@

The logic confirmed that certain kinds
of circumstance, act, goal tuples are too badly formed for the categorical imperative to logically 
apply to them. The realization of this subtle problem would have been incredibly difficult without 
computational tools. The syntax and typing of Isabelle/HOL forced me to bind the free-variable $M$
in the FUL in different ways and allowed me to quickly test many bindings. The discovery of this 
logical inconsistency then enabled a philosophical insight about which kinds of maxims make sense as 
practical principles. This is one way to do computational ethics: model a system in a logic, use 
computational tools to refine and debug the logic, and then use insights about the logic to derive 
insights about the ethical phenonema it is modelling. This procedure parallels the use of proofs in 
theoretical math to understand the mathematical objects they model.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
One potential problem with my formalization is that it does not use the modal nature of the system. 
All of the properties that the FUL investigates hold at all worlds, in effect removing the modal nature 
of the system. This approach simplifies logical and therefore computational complexity, improving 
performance. On the other hand, it doesn't use the full expressivity of DDL. If I run into problems 
later on, one option is to tweak the FUL to use this expressivity.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Application Tests%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
As with the naive formalization and Kroy's formalization, I will apply my testing framework to 
my custom formalization of the FUL. I will begin with some basic application tests. In these tests, 
I specify particular maxims as constants with no properties and gradually add properties to understand 
how the system handles different kinds of maxims.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Metaethical Tests%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Recall that metaethical tests test formal properties of the system that apply to any maxim, not 
just those specified in the application tests. In this section I adapt the metaethical tests developed 
in previous sections to my formalization of the categorical imperative. I preserved the philosophical 
goal of each test but modified them to test the stronger, richer notion of a maxim.

@@

%:%274=216%:%

@@

@@

%:%287=228%:%

@@

%:%290=230%:%
%:%291=231%:%
%:%292=231%:%
%:%293=232%:%
%:%295=233%:%
%:%296=234%:%
%:%299=236%:%
%:%300=237%:%
%:%301=238%:%
%:%302=239%:%
%:%303=240%:%
%:%304=241%:%
%:%305=242%:%
%:%306=243%:%
%:%307=244%:%
%:%308=245%:%
%:%309=246%:%
%:%310=247%:%
%:%311=248%:%
%:%312=249%:%
%:%313=250%:%
%:%314=251%:%
%:%315=252%:%
%:%316=253%:%
%:%317=254%:%
%:%318=255%:%
%:%319=256%:%
%:%320=257%:%
%:%321=258%:%
%:%322=259%:%
%:%323=260%:%
%:%325=262%:%
%:%326=262%:%
%:%327=263%:%
%:%329=264%:%
%:%330=265%:%
%:%331=265%:%
%:%332=266%:%
%:%333=267%:%
%:%334=267%:%
%:%336=268%:%
%:%337=269%:%
%:%338=270%:%
%:%346=272%:%
%:%358=274%:%
%:%359=275%:%
%:%360=276%:%
%:%361=277%:%
%:%362=278%:%
%:%363=279%:%
%:%365=282%:%
%:%366=282%:%
%:%368=283%:%
%:%369=284%:%
%:%370=285%:%
%:%371=286%:%
%:%372=286%:%
%:%373=287%:%
%:%374=288%:%
%:%375=288%:%
%:%377=288%:%
%:%381=288%:%
%:%382=288%:%
%:%383=289%:%
%:%384=289%:%
%:%385=289%:%
%:%394=291%:%
%:%395=292%:%
%:%396=293%:%
%:%397=294%:%
%:%398=295%:%
%:%399=296%:%
%:%400=297%:%
%:%401=298%:%
%:%402=299%:%
%:%403=300%:%
%:%404=301%:%
%:%405=302%:%
%:%406=303%:%
%:%407=304%:%
%:%408=305%:%
%:%409=306%:%
%:%410=307%:%
%:%412=309%:%
%:%413=309%:%
%:%414=310%:%
%:%416=311%:%
%:%417=312%:%
%:%418=312%:%
%:%419=313%:%
%:%420=314%:%
%:%421=314%:%

@@

%:%425=316%:%
%:%426=317%:%
%:%427=318%:%
%:%428=318%:%
%:%429=319%:%
%:%430=319%:%
%:%432=319%:%
%:%436=319%:%
%:%437=319%:%
%:%439=320%:%
%:%440=321%:%
%:%441=322%:%
%:%442=323%:%
%:%443=324%:%
%:%444=325%:%
%:%445=326%:%
%:%446=327%:%
%:%447=328%:%
%:%448=329%:%
%:%449=330%:%
%:%457=330%:%
%:%458=331%:%
%:%459=332%:%
%:%460=332%:%
%:%461=333%:%
%:%462=334%:%
%:%463=334%:%
%:%464=335%:%
%:%465=335%:%
%:%467=335%:%
%:%471=335%:%
%:%472=335%:%
%:%474=336%:%
%:%475=337%:%
%:%476=338%:%
%:%477=339%:%
%:%478=340%:%
%:%479=341%:%
%:%489=343%:%
%:%490=344%:%
%:%491=345%:%
%:%492=346%:%
%:%493=347%:%
%:%494=348%:%
%:%495=349%:%
%:%496=350%:%
%:%497=351%:%
%:%498=352%:%
%:%499=353%:%
%:%500=354%:%
%:%501=355%:%
%:%502=356%:%
%:%503=357%:%
%:%504=358%:%
%:%505=359%:%
%:%506=360%:%
%:%507=361%:%
%:%508=362%:%
%:%512=364%:%
%:%513=365%:%
%:%514=366%:%
%:%515=367%:%
%:%516=368%:%
%:%525=370%:%
%:%537=372%:%
%:%538=373%:%
%:%539=374%:%
%:%540=375%:%
%:%549=378%:%
%:%561=380%:%
%:%562=381%:%
%:%563=382%:%
%:%564=383%:%
%:%565=384%:%
%:%566=385%:%
%:%567=386%:%
%:%568=387%:%
%:%569=388%:%
%:%570=389%:%
%:%571=390%:%
%:%572=391%:%
%:%573=392%:%
%:%574=393%:%
%:%575=394%:%
%:%576=395%:%
%:%577=396%:%
%:%578=397%:%
%:%579=398%:%
%:%580=399%:%
%:%582=401%:%
%:%583=401%:%
%:%584=402%:%
%:%587=403%:%
%:%591=403%:%
%:%592=403%:%
%:%597=403%:%
%:%600=404%:%
%:%601=405%:%
%:%602=405%:%
%:%603=406%:%
%:%606=407%:%
%:%610=407%:%
%:%611=407%:%
%:%616=407%:%
%:%619=408%:%
%:%620=409%:%
%:%621=409%:%
%:%622=410%:%
%:%625=411%:%
%:%629=411%:%
%:%630=411%:%
%:%635=411%:%
%:%638=412%:%
%:%639=413%:%
%:%640=413%:%
%:%641=414%:%
%:%644=415%:%
%:%648=415%:%
%:%649=415%:%
%:%658=417%:%
%:%659=418%:%
%:%660=419%:%
%:%661=420%:%
%:%662=421%:%
%:%663=422%:%
%:%664=423%:%
%:%666=425%:%
%:%667=425%:%
%:%668=426%:%
%:%669=427%:%
%:%670=427%:%
%:%672=427%:%
%:%676=427%:%
%:%677=427%:%
%:%679=428%:%
%:%680=429%:%
%:%681=430%:%
%:%682=431%:%
%:%683=432%:%
%:%684=433%:%
%:%685=434%:%
%:%686=435%:%
%:%687=436%:%
%:%688=437%:%
%:%689=438%:%
%:%699=440%:%
%:%700=441%:%
%:%702=443%:%
%:%703=443%:%
%:%704=444%:%
%:%707=445%:%
%:%711=445%:%
%:%712=445%:%
%:%714=446%:%
%:%724=448%:%
%:%725=449%:%
%:%727=451%:%
%:%728=451%:%
%:%729=452%:%
%:%732=453%:%
%:%736=453%:%
%:%737=453%:%
%:%738=453%:%
%:%740=454%:%
%:%741=455%:%
%:%751=457%:%
%:%752=458%:%
%:%753=459%:%
%:%754=460%:%
%:%755=461%:%
%:%756=462%:%
%:%757=463%:%
%:%758=464%:%
%:%759=465%:%
%:%760=466%:%
%:%761=467%:%
%:%762=468%:%
%:%766=470%:%
%:%767=471%:%
%:%768=472%:%
%:%770=474%:%
%:%771=474%:%
%:%772=475%:%
%:%773=476%:%
%:%774=477%:%
%:%775=477%:%
%:%777=477%:%
%:%781=477%:%
%:%782=477%:%
%:%784=478%:%
%:%785=479%:%
%:%786=480%:%
%:%787=481%:%
%:%788=482%:%
%:%789=483%:%
%:%790=484%:%
%:%791=485%:%
%:%792=486%:%
%:%793=487%:%
%:%803=489%:%
%:%804=490%:%
%:%805=491%:%
%:%807=493%:%
%:%808=493%:%
%:%809=494%:%
%:%810=495%:%
%:%811=495%:%
%:%813=495%:%
%:%817=495%:%
%:%818=495%:%
%:%820=496%:%
%:%821=497%:%
%:%822=498%:%
%:%823=499%:%
%:%824=500%:%
%:%825=501%:%
%:%826=502%:%
%:%827=503%:%
%:%828=504%:%
%:%829=505%:%
%:%839=507%:%
%:%840=508%:%
%:%841=509%:%
%:%842=510%:%
%:%844=512%:%
%:%845=512%:%
%:%846=513%:%
%:%849=514%:%
%:%853=514%:%
%:%854=514%:%
%:%855=514%:%
%:%857=515%:%
%:%863=515%:%
%:%866=516%:%
%:%867=517%:%
%:%868=517%:%
%:%869=518%:%
%:%872=519%:%
%:%876=519%:%
%:%877=519%:%
%:%878=519%:%
%:%880=520%:%
%:%886=520%:%
%:%889=521%:%
%:%890=522%:%
%:%891=522%:%
%:%892=523%:%
%:%893=524%:%
%:%896=525%:%
%:%900=525%:%
%:%901=525%:%
%:%902=525%:%
%:%904=526%:%
%:%905=527%:%
%:%915=529%:%
%:%916=530%:%
%:%917=531%:%
%:%918=532%:%
%:%919=533%:%
%:%920=534%:%
%:%921=535%:%
%:%930=537%:%
%:%942=539%:%
%:%943=540%:%
%:%944=541%:%
%:%945=542%:%
%:%947=544%:%
%:%948=544%:%
%:%949=545%:%
%:%950=546%:%
%:%951=546%:%
%:%953=546%:%
%:%957=546%:%
%:%958=546%:%
%:%960=547%:%
%:%961=548%:%
%:%962=549%:%
%:%963=550%:%
%:%964=551%:%
%:%965=552%:%
%:%966=553%:%
%:%967=554%:%
%:%968=555%:%
%:%969=556%:%
%:%970=557%:%
%:%971=557%:%

>>>>

If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ universalized{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}universalized\ {\isasymequiv}\ {\isasymlambda}M{\isachardot}\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ W\ M\ p\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ holds{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}holds\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ c{\isachardoublequoteclose}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ not{\isacharunderscore}universalizable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}not{\isacharunderscore}universalizable\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}{\isasymnot}\ {\isacharparenleft}holds\ M\ w{\isacharparenright}{\isacharparenright}\ {\isasymor}\ {\isacharparenleft}universalized\ M\ \ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}E\ M\ s{\isacharparenright}{\isacharparenright}{\isacharparenright}w{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{The formula above reads ``at world $w$, if M is universalized and M is acted on (i.e. the circumstances 
of M hold), then M is not effective."

Notice that the antecedent specifies that the circumstances hold at the given world. 
When evaluating if a maxim is universalizable or not, we want to ignore worlds where the circumstance 
do not hold. At these worlds, the maxim is trivially effective and thus trivially universalizable. If we didn't exclude such worlds from 
consideration, a maxim with circumstances that ever fail to hold would be universalizable. Clearly 
this is not a desirable conclusion, since maxims like ``When you need money, lie to get easy money"
would be universalizable.%

@@

\ imagine{\isacharunderscore}a{\isacharunderscore}world{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}imagine{\isacharunderscore}a{\isacharunderscore}world\ {\isasymequiv}\ {\isasymlambda}M{\isachardot}\ {\isacharparenleft}{\isasymexists}w{\isachardot}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ {\isacharparenleft}W\ M\ p{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isamarkupcmt{This abbreviation formalizes the idea that, for any maxim, some world where exist where the maxim 
is universally willed.%

@@

\ not{\isacharunderscore}contradictory{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}not{\isacharunderscore}contradictory\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ {\isacharparenleft}{\isasymforall}p\ w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}c\ \isactrlbold {\isasymand}\ {\isacharparenleft}a\ p{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbottom}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \isakeyword{where}\ test{\isacharcolon}{\isachardoublequoteopen}{\isasymforall}M{\isachardot}\ not{\isacharunderscore}contradictory\ M\ {\isasymlongrightarrow}\ imagine{\isacharunderscore}a{\isacharunderscore}world\ M{\isachardoublequoteclose}%

@@

\ O{\isacharunderscore}diamond\isanewline
\ \ \isacommand{by}\isamarkupfalse%
\ force%

@@

The logic confirmed that certain kinds
of circumstance, act, goal tuples are too badly formed for the categorical imperative to logically 
apply to them. The realization of this subtle problem would have been incredibly difficult without 
computational tools. The syntax and typing of Isabelle/HOL forced me to bind the free-variable $M$
in the FUL in different ways and allowed me to quickly test many bindings. The discovery of this 
logical inconsistency then enabled a philosophical insight about which kinds of maxims make sense as 
practical principles. This is one way to do computational ethics: model a system in a logic, use 
computational tools to refine and debug the logic, and then use insights about the logic to derive 
insights about the ethical phenonema it is modelling. This procedure parallels the use of proofs in 
theoretical math to understand the mathematical objects they model.%
One potential problem with my formalization is that it does not use the modal nature of the system. 
All of the properties that the FUL investigates hold at all worlds, in effect removing the modal nature 
of the system. This approach simplifies logical and therefore computational complexity, improving 
performance. On the other hand, it doesn't use the full expressivity of DDL. If I run into problems 
later on, one option is to tweak the FUL to use this expressivity.%
\isamarkupsubsection{Application Tests%
As with the naive formalization and Kroy's formalization, I will apply my testing framework to 
my custom formalization of the FUL. I will begin with some basic application tests. In these tests, 
I specify particular maxims as constants with no properties and gradually add properties to understand 
how the system handles different kinds of maxims.%
\isacommand{consts}\isamarkupfalse%
\ when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash{\isacharcolon}{\isacharcolon}t\isanewline
\isacommand{consts}\isamarkupfalse%
\ lie{\isacharcolon}{\isacharcolon}os\isanewline
\isacommand{consts}\isamarkupfalse%
\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharcolon}{\isacharcolon}t\isanewline
\ lie{\isacharunderscore}maxim{\isacharcolon}{\isacharcolon}maxim\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}lie{\isacharunderscore}maxim\ {\isasymequiv}\ {\isacharparenleft}when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash{\isacharcomma}\ lie{\isacharcomma}\ to{\isacharunderscore}get{\isacharunderscore}easy{\isacharunderscore}cash{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}s{\isachardot}\ lie{\isacharparenleft}s{\isacharparenright}\ w{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
\ lying{\isacharunderscore}bad{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ everyone{\isacharunderscore}can{\isacharprime}t{\isacharunderscore}lie\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}when{\isacharunderscore}strapped{\isacharunderscore}for{\isacharunderscore}cash\ cw{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ not{\isacharunderscore}universalizable\ lie{\isacharunderscore}maxim\ s{\isachardoublequoteclose}\isanewline
\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
\ auto%
\ test{\isadigit{6}}{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ not{\isacharunderscore}universalizable\ lie{\isacharunderscore}maxim\ s{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ lie{\isacharunderscore}maxim\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}s{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}prohibited\ lie{\isacharunderscore}maxim\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ FUL\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
Action is impossible%
Maxim is bad under PC interp%
\isamarkupsubsection{Metaethical Tests%
Recall that metaethical tests test formal properties of the system that apply to any maxim, not 
just those specified in the application tests. In this section I adapt the metaethical tests developed 
in previous sections to my formalization of the categorical imperative. I preserved the philosophical 
goal of each test but modified them to test the stronger, richer notion of a maxim.

@@

%:%273=216%:%
%:%274=217%:%

@@

%:%276=218%:%

@@

%:%286=227%:%
%:%287=227%:%

@@

%:%290=229%:%
%:%291=230%:%
%:%293=231%:%
%:%294=232%:%
%:%295=232%:%
%:%296=233%:%
%:%297=234%:%
%:%298=234%:%
%:%299=235%:%
%:%300=236%:%
%:%301=237%:%
%:%302=237%:%
%:%304=239%:%
%:%305=240%:%
%:%306=241%:%
%:%307=242%:%
%:%308=243%:%
%:%309=244%:%
%:%310=245%:%
%:%311=246%:%
%:%313=248%:%
%:%314=248%:%
%:%315=249%:%
%:%316=250%:%
%:%317=251%:%
%:%318=251%:%
%:%319=252%:%
%:%321=253%:%
%:%322=254%:%
%:%325=256%:%
%:%326=257%:%
%:%327=258%:%
%:%328=259%:%
%:%329=260%:%
%:%330=261%:%
%:%331=262%:%
%:%332=263%:%
%:%333=264%:%
%:%334=265%:%
%:%335=266%:%
%:%336=267%:%
%:%337=268%:%
%:%338=269%:%
%:%339=270%:%
%:%340=271%:%
%:%341=272%:%
%:%342=273%:%
%:%343=274%:%
%:%344=275%:%
%:%345=276%:%
%:%346=277%:%
%:%347=278%:%
%:%348=279%:%
%:%349=280%:%
%:%351=282%:%
%:%352=282%:%
%:%353=283%:%
%:%355=284%:%
%:%356=285%:%
%:%357=285%:%
%:%358=286%:%
%:%359=287%:%
%:%360=287%:%
%:%362=288%:%
%:%363=289%:%
%:%364=290%:%
%:%372=292%:%
%:%384=294%:%
%:%385=295%:%
%:%386=296%:%
%:%387=297%:%
%:%388=298%:%
%:%389=299%:%
%:%391=302%:%
%:%392=302%:%
%:%394=303%:%
%:%395=304%:%
%:%396=305%:%
%:%397=306%:%
%:%398=306%:%
%:%399=307%:%
%:%400=308%:%
%:%401=308%:%
%:%403=308%:%
%:%407=308%:%
%:%408=308%:%
%:%409=309%:%
%:%410=309%:%
%:%419=311%:%
%:%420=312%:%
%:%421=313%:%
%:%422=314%:%

@@

%:%425=317%:%
%:%426=318%:%
%:%427=319%:%
%:%428=320%:%
%:%429=321%:%
%:%430=322%:%
%:%431=323%:%
%:%432=324%:%
%:%433=325%:%
%:%434=326%:%
%:%435=327%:%
%:%437=329%:%
%:%438=329%:%
%:%439=330%:%
%:%441=331%:%
%:%442=332%:%
%:%443=332%:%
%:%444=333%:%
%:%445=334%:%
%:%446=334%:%
%:%448=335%:%
%:%449=336%:%
%:%450=336%:%
%:%451=337%:%
%:%452=338%:%
%:%453=338%:%
%:%454=339%:%
%:%455=339%:%
%:%457=339%:%
%:%461=339%:%
%:%462=339%:%
%:%464=340%:%
%:%465=341%:%
%:%466=342%:%
%:%467=343%:%
%:%468=344%:%
%:%469=345%:%
%:%470=346%:%
%:%471=347%:%
%:%472=348%:%
%:%473=349%:%
%:%474=350%:%
%:%482=350%:%
%:%483=351%:%
%:%484=352%:%
%:%485=352%:%
%:%486=353%:%
%:%487=354%:%
%:%488=354%:%
%:%489=355%:%
%:%490=355%:%
%:%492=355%:%
%:%496=355%:%
%:%497=355%:%
%:%499=356%:%
%:%500=357%:%
%:%501=358%:%
%:%502=359%:%
%:%503=360%:%
%:%504=361%:%
%:%514=363%:%
%:%515=364%:%
%:%516=365%:%
%:%517=366%:%
%:%518=367%:%
%:%519=368%:%
%:%520=369%:%
%:%521=370%:%
%:%522=371%:%
%:%523=372%:%
%:%524=373%:%
%:%525=374%:%
%:%526=375%:%
%:%527=376%:%
%:%528=377%:%
%:%529=378%:%
%:%530=379%:%
%:%531=380%:%
%:%532=381%:%
%:%533=382%:%
%:%537=384%:%
%:%538=385%:%
%:%539=386%:%
%:%540=387%:%
%:%541=388%:%
%:%550=390%:%
%:%562=392%:%
%:%563=393%:%
%:%564=394%:%
%:%565=395%:%
%:%567=397%:%
%:%568=397%:%
%:%569=398%:%
%:%570=398%:%
%:%571=399%:%
%:%572=399%:%
%:%573=400%:%
%:%574=400%:%
%:%575=401%:%
%:%576=402%:%
%:%577=403%:%
%:%578=403%:%
%:%579=404%:%
%:%580=405%:%
%:%581=406%:%
%:%582=406%:%
%:%583=407%:%
%:%584=408%:%
%:%585=409%:%
%:%588=410%:%
%:%592=410%:%
%:%593=410%:%
%:%594=410%:%
%:%599=410%:%
%:%602=411%:%
%:%603=412%:%
%:%604=412%:%
%:%605=413%:%
%:%606=414%:%
%:%607=415%:%
%:%610=416%:%
%:%614=416%:%
%:%615=416%:%
%:%616=416%:%
%:%625=420%:%
%:%629=422%:%
%:%638=424%:%
%:%650=426%:%
%:%651=427%:%
%:%652=428%:%
%:%653=429%:%
%:%654=430%:%
%:%655=431%:%
%:%656=432%:%
%:%657=433%:%
%:%658=434%:%
%:%659=435%:%
%:%660=436%:%
%:%661=437%:%
%:%662=438%:%
%:%663=439%:%
%:%664=440%:%
%:%665=441%:%
%:%666=442%:%
%:%667=443%:%
%:%668=444%:%
%:%669=445%:%
%:%671=447%:%
%:%672=447%:%
%:%673=448%:%
%:%676=449%:%
%:%680=449%:%
%:%681=449%:%
%:%686=449%:%
%:%689=450%:%
%:%690=451%:%
%:%691=451%:%
%:%692=452%:%
%:%695=453%:%
%:%699=453%:%
%:%700=453%:%
%:%705=453%:%
%:%708=454%:%
%:%709=455%:%
%:%710=455%:%
%:%711=456%:%
%:%714=457%:%
%:%718=457%:%
%:%719=457%:%
%:%724=457%:%
%:%727=458%:%
%:%728=459%:%
%:%729=459%:%
%:%730=460%:%
%:%733=461%:%
%:%737=461%:%
%:%738=461%:%
%:%747=463%:%
%:%748=464%:%
%:%749=465%:%
%:%750=466%:%
%:%751=467%:%
%:%752=468%:%
%:%753=469%:%
%:%755=471%:%
%:%756=471%:%
%:%757=472%:%
%:%758=473%:%
%:%759=473%:%
%:%761=473%:%
%:%765=473%:%
%:%766=473%:%
%:%768=474%:%
%:%769=475%:%
%:%770=476%:%
%:%771=477%:%
%:%772=478%:%
%:%773=479%:%
%:%774=480%:%
%:%775=481%:%
%:%776=482%:%
%:%777=483%:%
%:%778=484%:%
%:%788=486%:%
%:%789=487%:%
%:%791=489%:%
%:%792=489%:%
%:%793=490%:%
%:%796=491%:%
%:%800=491%:%
%:%801=491%:%
%:%803=492%:%
%:%813=494%:%
%:%814=495%:%
%:%816=497%:%
%:%817=497%:%
%:%818=498%:%
%:%821=499%:%
%:%825=499%:%
%:%826=499%:%
%:%827=499%:%
%:%829=500%:%
%:%830=501%:%
%:%840=503%:%
%:%841=504%:%
%:%842=505%:%
%:%843=506%:%
%:%844=507%:%
%:%845=508%:%
%:%846=509%:%
%:%847=510%:%
%:%848=511%:%
%:%849=512%:%
%:%850=513%:%
%:%851=514%:%
%:%855=516%:%
%:%856=517%:%
%:%857=518%:%
%:%859=520%:%
%:%860=520%:%
%:%861=521%:%
%:%862=522%:%
%:%863=523%:%
%:%864=523%:%
%:%866=523%:%
%:%870=523%:%
%:%871=523%:%
%:%873=524%:%
%:%874=525%:%
%:%875=526%:%
%:%876=527%:%
%:%877=528%:%
%:%878=529%:%
%:%879=530%:%
%:%880=531%:%
%:%881=532%:%
%:%882=533%:%
%:%892=535%:%
%:%893=536%:%
%:%894=537%:%
%:%896=539%:%
%:%897=539%:%
%:%898=540%:%
%:%899=541%:%
%:%900=541%:%
%:%902=541%:%
%:%906=541%:%
%:%907=541%:%
%:%909=542%:%
%:%910=543%:%
%:%911=544%:%
%:%912=545%:%
%:%913=546%:%
%:%914=547%:%
%:%915=548%:%
%:%916=549%:%
%:%917=550%:%
%:%918=551%:%
%:%928=553%:%
%:%929=554%:%
%:%930=555%:%
%:%931=556%:%
%:%933=558%:%
%:%934=558%:%
%:%935=559%:%
%:%938=560%:%
%:%942=560%:%
%:%943=560%:%
%:%944=560%:%
%:%946=561%:%
%:%952=561%:%
%:%955=562%:%
%:%956=563%:%
%:%957=563%:%
%:%958=564%:%
%:%961=565%:%
%:%965=565%:%
%:%966=565%:%
%:%967=565%:%
%:%969=566%:%
%:%975=566%:%
%:%978=567%:%
%:%979=568%:%
%:%980=568%:%
%:%981=569%:%
%:%982=570%:%
%:%985=571%:%
%:%989=571%:%
%:%990=571%:%
%:%991=571%:%
%:%993=572%:%
%:%994=573%:%
%:%1004=575%:%
%:%1005=576%:%
%:%1006=577%:%
%:%1007=578%:%
%:%1008=579%:%
%:%1009=580%:%
%:%1010=581%:%
%:%1019=583%:%
%:%1031=585%:%
%:%1032=586%:%
%:%1033=587%:%
%:%1034=588%:%
%:%1036=590%:%
%:%1037=590%:%
%:%1038=591%:%
%:%1039=592%:%
%:%1040=592%:%
%:%1042=592%:%
%:%1046=592%:%
%:%1047=592%:%
%:%1049=593%:%
%:%1050=594%:%
%:%1051=595%:%
%:%1052=596%:%
%:%1053=597%:%
%:%1054=598%:%
%:%1055=599%:%
%:%1056=600%:%
%:%1057=601%:%
%:%1058=602%:%
%:%1059=603%:%
%:%1060=603%:%
